tidy_author

### 2021-11-21 tidy_author.Rmd
Manually inspecting and tidying the author column.

ctvdf <- ctvs %>% 
  unnest_longer(pkgs) %>% 
  left_join(select(db, Package, Author, Depends, Imports, Suggests), 
            by = c("pkgs" = "Package")) %>% 
  mutate(across(c(Depends, Imports, Suggests),
                ~str_split(.x, ", "))) %>% 
  mutate(across(c(Depends, Imports, Suggests),
                ~map(.x, function(apkg) str_extract(apkg, "^[A-Za-z0-9]+")))) %>%
  mutate(author_tidy = str_replace_all(Author, "\\s+", " "),
         author_tidy = str_replace_all(author_tidy, "<.*?>", ""),
         author_tidy = str_replace_all(author_tidy, "\\[.*?\\]", ""),
         author_tidy = str_replace_all(author_tidy, "\\(.*?\\)", ""),
         author_tidy = str_replace_all(author_tidy, "(&| and)", ","),
         author_tidy = str_replace_all(author_tidy, "\\(.*\\)", ""),
         author_tidy = str_replace_all(author_tidy, "\\.*$", ""),
         author_tidy = str_replace_all(author_tidy, ",,", ","),
         author_tidy = str_replace_all(author_tidy, " \\)", ""),
         author_tidy = str_replace_all(author_tidy, "\\\\", ""),
         author_tidy = str_replace_all(author_tidy, "\\s*,", ","),
         author_tidy = str_squish(author_tidy))

@@

library(yaml)

ctvdf_sentences <- ctvdf %>%
  filter(str_detect(author_tidy, "riginal") | 
           str_detect(author_tidy, " by ") | 
           str_detect(author_tidy, "with ") |
           str_detect(author_tidy, " under ") | 
           str_detect(author_tidy, "sole") | 
           str_detect(author_tidy,"written") | 
           str_detect(author_tidy, "port") | 
           str_detect(author_tidy, " work")|
           str_detect(author_tidy,"suggestion") | 
           str_detect(author_tidy,"code") | 
           str_detect(author_tidy, " from ")) %>%
  select(pkgs, author_tidy) %>%
  distinct()

@@

# manually tidy the author in sentences due to the variability

@@

@@

@@

@@

@@

@@

@@

@@

                    "Stéphane Dray, Anne-Béatrice Dufour, Jean Thioulouse, with contributions from Thibaut Jombart, Sandrine Pavoine, Jean R. Lobry, Sébastien Ollier, Daniel Borcard, Pierre Legendre, Stéphanie Bougeard, Aurélie Siberchicot, Daniel Chessel",

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

                    "Berwin A. Turlach, Andreas Weingessel, Cleve Moler)",

@@

@@

@@

@@

                    "Kenneth Knoblauch, Laurence T. Maloney, Laurence T. Maloney, J. N. Yang",

@@

@@

@@

@@

@@

@@

@@

@@

@@

ctvdf_author <- left_join(ctvdf, tidy_aut2, by = "pkgs") %>%
  mutate(tidy_aut = if_else(is.na(tidy_aut), author_tidy, tidy_aut),
         tidy_aut = str_replace_all(tidy_aut, ",,", ","))
```

>>>>

ctvdf <- ctvs %>% 
  unnest_longer(pkgs) %>% 
  left_join(select(db, Package, Author, Depends, Imports, Suggests), 
            by = c("pkgs" = "Package")) %>% 
  mutate(across(c(Depends, Imports, Suggests),
                ~str_split(.x, ", "))) %>% 
  mutate(across(c(Depends, Imports, Suggests),
                ~map(.x, function(apkg) str_extract(apkg, "^[A-Za-z0-9]+")))) %>%
  mutate(author_tidy = str_replace_all(Author, "\\s+", " "),
         author_tidy = str_replace_all(author_tidy, "<.*?>", ""),
         author_tidy = str_replace_all(author_tidy, "\\[.*?\\]", ""),
         author_tidy = str_replace_all(author_tidy, "\\(.*?\\)", ""),
         author_tidy = str_replace_all(author_tidy, "\\(.*\\)", ""),
         author_tidy = str_replace_all(author_tidy, "(&| and)", ","),
         author_tidy = str_replace_all(author_tidy, "\\.*$", ""),
         author_tidy = str_replace_all(author_tidy, ",,", ","),
         author_tidy = str_replace_all(author_tidy, " \\)", ""),
         author_tidy = str_replace_all(author_tidy, "\\\\", ""),
         author_tidy = str_replace_all(author_tidy, "\\s*,", ","),
         author_tidy = str_squish(author_tidy))

@@

ctvdf_sentences <- ctvdf %>%
  filter(str_detect(author_tidy, "riginal") | 
           str_detect(author_tidy, " by ") | 
           str_detect(author_tidy, "with ") |
           str_detect(author_tidy, " under ") | 
           str_detect(author_tidy, "sole") | 
           str_detect(author_tidy,"written") | 
           str_detect(author_tidy, "port") | 
           str_detect(author_tidy, " work")|
           str_detect(author_tidy,"suggestion") | 
           str_detect(author_tidy,"code") | 
           str_detect(author_tidy, " from ") |
           str_detect(author_tidy, " for ") |
           str_detect(author_tidy, "FORTRAN") |
           str_detect(pkgs, "fBasics") |
           str_detect(pkgs, "RobPer") |
           str_detect(pkgs, "dfpk") |
           str_detect(pkgs, "nor1") |
           str_detect(pkgs, "mkin") |
           str_detect(author_tidy, "Imperial College of Science, Technology, Medicine") |
           str_detect(pkgs, "RH2") |
           str_detect(pkgs, "DPQ") |
           str_detect(pkgs, "RDieHarder") |
           str_detect(pkgs, "sfsmisc") |
           str_detect(pkgs, "oce") |
           str_detect(pkgs, "DiceKriging") |
           str_detect(pkgs, "fracdiff") |
           str_detect(pkgs, "RcppQuantuccia") |
           str_detect(pkgs, "dbstats") |
           str_detect(pkgs, "drake") |
           str_detect(pkgs, "proffer") |
           str_detect(pkgs, "targets") |
           str_detect(pkgs, "GSODR") |
           str_detect(pkgs, "MODIStsp") |
           str_detect(pkgs, "baggr") |
           str_detect(pkgs, "EvidenceSynthesis") |
           str_detect(pkgs, "SAMURAI") |
           str_detect(pkgs, "crfsuite") |
           str_detect(pkgs, "udpipe") |
           str_detect(pkgs, "Rmpfr") |
           str_detect(pkgs, "EdSurvey") |
           str_detect(pkgs, "rrcov3way") |
           str_detect(pkgs, "RcppDE") |
           str_detect(pkgs, "irr") |
           str_detect(pkgs, "irtDemo") |
           str_detect(pkgs, "kcirt") |
           str_detect(pkgs, "MLCIRTwithin") |
           str_detect(pkgs, "MultiLCIRT") |
           str_detect(pkgs, "HTMLUtils") |
           str_detect(pkgs, "workflowr") |
           str_detect(pkgs, "landscapemetrics") |
           str_detect(pkgs, "bentcableAR") |
           str_detect(pkgs, "BMTAR") |
           str_detect(pkgs, "MARSS") |
           str_detect(pkgs, "MultipleBubbles")) %>%
  select(pkgs, author_tidy) %>%
  distinct()

@@

```

```{r}
# manually tidy the author in sentences due to the variability

@@

                    "Anita M. Thieler, Jonathan Rathjens, Roland Fried, Brenton R. Clarke, Uwe Ligges, Matias Salibian-Barrera, Gert Willems, Victor Yohai",

@@

                    "Artemis Toumazi, Sarah Zohar, Moreno Ursino, Trustees of Columbia University, French National Institute of Health and Medical Research",
                    "Charlie Casper, Oscar A. Perez",

@@

                    "Martin Maechler, Friedrich Leisch, Erik Jørgensen",
                    "Adelchi Azzalini, Giovanna Menardi, Adelchi Azzalini, Tiziana Rosolin", 
                    "G. Grothendieck, Thomas Mueller",
                    "Rich FitzJohn, Wes Hinsley, Imperial College of Science, Technology and Medicine",
                    "Johannes Ranke, Katrin Lindenberger, René Lehmann, Eurofins Regulatory AG",

@@

                    "Martin Maechler, Morten Welinder, Wolfgang Viechtbauer, Ross Ihaka, Marius Hofert, R-core, R Foundation",

@@

                    "Diethelm Wuertz, Tobias Setz, Yohan Chalabi, Martin Maechler",

@@

                    "Dirk Eddelbuettel, Robert G Brown, David Bauer",
                    "Martin Maechler, Werner Stahel, Andreas Ruckstuhl, Christian Keller, Kjetil Halvorsen, Alain Hauser, iChristoph Buser, Lorenz Gygax, Bill Venables, Tony Plate, Isabelle Flückiger, Marcel Wolbers, Markus Keller, Sandrine Dudoit, Jane Fridlyand, Greg Snow, Henrik Aa. Nielsen, Vincent Carey, Ben Bolker, Philippe Grosjean, Frédéric Ibanez, Caterina Savi, Charles Geyer, Jens Oehlschlägel",

@@

                    "Douglas Bates, Martin Maechler, Timothy A. Davis, Jens Oehlschlägel, Jason Riedy, Regents of the University of California, R Core Team",

@@

                    "Stéphane Dray, Anne-Béatrice Dufour, Jean Thioulouse, Thibaut Jombart, Sandrine Pavoine, Jean R. Lobry, Sébastien Ollier, Daniel Borcard, Pierre Legendre, Stéphanie Bougeard, Aurélie Siberchicot, Daniel Chessel",

@@

                    "Dan Kelley, Clark Richards, Chantelle Layton, British Geological Survey",

@@

                    "Olivier Roustant, David Ginsbourger, Yves Deville, Clement Chevalier, Yann Richet",

@@

                    "Martin Maechler, Chris Fraley, Friedrich Leisch, Valderio Reisen, Artur Lemonte, Rob Hyndman",

@@

                    "Dirk Eddelbuettel",
                    "Eva Boj, Adria Caballe, Pedro Delicado, Josep Fortiana",

@@

                    "William Michael Landau, Alex Axthelm, Jasper Clarkberg, Kirill Müller, Ben Bond-Lamberty, Tristan Mahr, Miles McBain, Noam Ross, Ellis Hughes, Matthew Mark Strasiotto, Ben Marwick, Peter Slaughter, Eli Lilly and Company",
                    "William Michael Landau, Eli Lilly and Company",
                    "William Michael Landau, Matthew T. Warkentin, Samantha Oliver, Tristan Mahr, Eli Lilly and Company",
                    "David Bronaugh",

@@

                    "Adam H. Sparks, Tomislav Hengl, Andrew Nelson, Hugh Parsonage, Taras Kaduk, Gwenael Giboire, Łukasz Pawlik, Ross Darnell, Tyler Widdison",
                    "Lorenzo Busetto, Luigi Ranghetti, Leah Wasser, Jeff Hanson, Babak Naimi",

@@

                    "Tobias Pilz, Potsdam Institute for Climate Impact Research",
                    "Ernest Guevarra, Valid International, Water and Sanitation for the Urban Poor",

@@

                    "Witold Wiecek, Rachael Meager, Brice Green, Trustees of Columbia University",

@@

                    "Martijn Schuemie, Marc A. Suchard, Observational Health Data Science and Informatics",
                    "Noory Y. Kim, Shrikant I. Bangdiwala, Gerald Gartlehner",

@@

                    "Steven M. Boker, Michael C. Neale, Hermine H. Maes, Michael J. Wilde, Michael Spiegel, Timothy R. Brick, Ryne Estabrook, Timothy C. Bates, Paras Mehta, Timo von Oertzen, Ross J. Gore, Michael D. Hunter, Daniel C. Hackett, Julian Karch, Andreas M. Brandmaier, Joshua N. Pritikin, Mahsa Zahery, Robert M. Kirkpatrick, Yang Wang, Ben Goodrich, Charles Driver, Massachusetts Institute of Technology, S. G. Johnson, Association for Computing Machinery, Dieter Kraft, Stefan Wilhelm, Sarah Medland, Carl F. Falk, Matt Keller, Manjunath B G, The Regents of the University of California, Lester Ingber, Wong Shao Voon, Juan Palacios, Jiang Yang, Gael Guennebaud, Jitse Niesen",

@@

                    "Jan Wijffels, BNOSAC, Naoaki Okazaki, Bob Jenkins, Jorge Nocedal, Jesse Long",

@@

                    "Jan Wijffels, BNOSAC, , Milan Straka, Jana Straková, Institute of Formal and Applied Linguistics, Faculty of Mathematics and Physics, Charles University in Prague",
                    "Hiroshi Akima, Albrecht Gebhardt, Thomas Petzold, Martin Maechler, YYYY Association for Computing Machinery, Inc.",

@@

                    "Yixuan Qiu, Jiali Mei, authors of the ARPACK library",
                    "Douglas Bates, Dirk Eddelbuettel, Romain Francois, Yixuan Qiu",
                    "Martin Maechler, Richard M. Heiberger, John C. Nash, Hans W. Borchers",

@@

                    "Paul Bailey, Ahmad Emad, Huade Huo, Michael Lee, Yuqi Liao, Alex Lishinski, Trang Nguyen, Qingshu Xie, Jiao Yu, Ting Zhang, Eric Buehler, Sun-joo Lee, Emmanuel Sikali, Jeppe Bundsgaard, Ren C'deBaca, Anders Astrup Christensen",

@@

                    "Valentin Todorov, Maria Anna Di Palma, Michele Gallo",

@@

                    "Berwin A. Turlach, Andreas Weingessel, Cleve Moler",

@@

                    "Dirk Eddelbuettel",

@@

                    "Matthias Gamer, Jim Lemon, Ian Fellows, Puspendra Singh",
                    "Metin Bulus, Wes Bonifay",

@@

                    "Dave Zes, Jimmy Lewis, Dana Landis",

@@

                    "Francesco Bartolucci, Silvia Bacci",
                    "Kenneth Knoblauch, Laurence T. Maloney, J. N. Yang",
                    "Francesco Bartolucci, Silvia Bacci, Michela Gnaldi",

@@

                    "Markus Loecher",
                    "Rich FitzJohn, Robert Ashton, Alex Hill, Martin Eden, Wes Hinsley, Emma Russell, James Thompson, Imperial College of Science, Technology and Medicine",

@@

                    "John Blischak, Peter Carbonetto, Matthew Stephens, Luke Zappia, Pierre Formont, Tim Trice, Jiaxiang Li, Michael J. Kane, Anh Tran, Sydney Purdue",

@@

                    "Martin Maechler, Werner A. Stahel, Rolf Turner, Ueli Oetliker, Tobias Schoch",

@@

                    "Douglas Nychka, Reinhard Furrer, John Paige, Stephan Sain, Florian Gerber, Matthew Iverson, University Corporation for Atmospheric Research",
                    "Rafael H. M. Pereira, Caio Nogueira Goncalves, Paulo Henrique Fernandes de Araujo, Guilherme Duarte Carvalho, Rodrigo Almeida de Arruda, Igor Nascimento, Barbara Santiago Pedreira da Costa, Welligtton Silva Cavedo, Pedro R. Andrade, Alan da Silva, Carlos Kauê Vieira Braga, Carl Schmertmann, Alessandro Samuel-Rosa, Daniel Ferreira, Ipea-Institue for Applied Economic Research", 

@@

                    "Maximillian H.K. Hesselbarth, Marco Sciaini, Jakub Nowosad, Sebastian Hanss, Laura J. Graham, Jeffrey Hollister, Kimberly A. With, Florian Privé, Project Nayuki, Matt Strimas-Mackey",

@@

                    "Andrea Gilardi, Robin Lovelace, Barry Rowlingson, Salva Fernández, Nicholas Potter",
                    "Robert J. Hijmans, Jacob van Etten, Michael Sumner, Joe Cheng, Dan Baston, Andrew Bevan, Roger Bivand, Lorenzo Busetto, Mort Canty, Ben Fasoli, David Forrest, Aniruddha Ghosh, Duncan Golicher, Josh Gray, Jonathan A. Greenberg, Paul Hiemstra, Kassel Hingee, Institute for Mathematics Applied Geosciences, Charles Karney, Matteo Mattiuzzi, Steven Mosher, Babak Naimi, Jakub Nowosad, Edzer Pebesma, Oscar Perpinan Lamigueiro, Etienne B. Racine, Barry Rowlingson, Ashton Shortridge, Bill Venables, Rafael Wueest",

@@

                    "Grace Chiu, CSIRO",
                    "Valeria Bejarano Salcedo, Sergio Alejandro Calderon Villanueva, Andrey Duvan Rincon Torres",

@@

                    "Eli Holmes, Eric Ward, Mark Scheuerell, Kellie Wills, NOAA",
                    "Pedro Araujo, Gustavo Lacerda, Peter C.B. Phillips, Shu-Ping Shi",

@@

ctvdf_author <- left_join(ctvdf, tidy_aut2, by = "pkgs") %>%
  mutate(tidy_aut = if_else(is.na(tidy_aut), author_tidy, tidy_aut),
         tidy_aut = str_replace_all(tidy_aut, ",,", ","))

#write_csv(ctvdf_author, "author_pkg.csv")
```
